Gromov--Witten theory of hypersurfaces in genus one

### 2019-03-01 GenusOneRelativeMaps.tex
removed incorrect step 4 recursion description

If such a relative marking does not exist, we will instead compute the invariant by recursing on the following space:
\begin{equation*} \VZ_{1,\alpha \cup (0,0)}(P|Y_0+Y_\infty,\beta)_{\Gm}. \end{equation*}
We denote the newly-introduced markings by $x_0$ and $y$. Choose a negative-tangency marking $x_1$ and consider the insertion $\tilde\gamma$ obtained from $\gamma$ by replacing every $\ev_1^\st$ by $\ev_0^\st$ and introducing $\fgt_{x_1}^\st$ everywhere.

Following \cite{EKatz}, there is a line bundle $L_{y}^{\neq\operatorname{bot}}$ equipped with a section whose vanishing locus $\Dcal(y)$ consists of boundary strata where the marking $y$ is not mapped into the bottom level of the expansion.\footnote{(Navid) Can we actually find a tropical description of this} The first Chern class of this line bundle is given by $\Psi_\infty + \ev_y^\st Y$ and $\Psi_\infty$ may be identified with $\alpha_2 \hat\psi_2 + \ev_2^\st Y$ where $x_2$ is any positive-tangency marking. Here $\hat\psi_2$ is a \emph{non-collapsed psi class} (recall that previously all our psi classes have been collapsed). Multiplying this by the insertion $\tilde\gamma \cdot \fgt_{x_1}^\st y$ we obtain:
\begin{equation}\label{step 4 recursion} \left( \alpha_2 \hat\psi_2 + \ev_2^\st Y + \ev_y^\st Y \right) \tilde\gamma \cdot \fgt_{x_1}^\st \psi_y \cap [\VZ_{1,\alpha \cup (0,0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cdot \fgt_{x_1}^\st \psi_y \cap [\Dcal(y)].\end{equation}
Start by examining the left-hand side; everything is pulled back along $\fgt_{x_1}$ except for $\hat\psi_2$. The difference between $\hat\psi_2$ and $\psi_2$ is given by the locus where $x_2$ belongs to a trivial bubble. In this case the curve must split into a number of pieces, and these are all known recursively except perhaps when all of the genus and degree is supported on one of these pieces $C^\prime$. When this happens we distinguish two cases, depending on whether $C^\prime$ is mapped into the top or the bottom piece of the expansion.

In the former case, we have a special reduced rubber invariant with the same degree and strictly fewer relative markings, so this is recursively known. In the latter case we must have $x_1 \in C^\prime$ and since all the insertions are pulled back along $\fgt_{x_1}$ we may apply the projection formula to identify the contribution with an absolute invariant of $Y$. Note that this absolute invariant may have more than $n$ markings (since $n$ is only the number of \emph{relative} markings) but the structure of the recursion is such that we are assuming we have computed \emph{all} absolute invariants of $Y$ of degree $d$. So this term is recursively known.

Thus, up to recursively known terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}. In the same vein, the difference between $\psi_2$ and $\fgt_{x_1}^\st \psi_2$ is given by the locus where $x_1$ and $x_2$ are contained on a collapsed rational bubble. In this case the contribution of this locus is given by a special rubber invariant with $n-2$ relative markings, and hence is recursively known. So we may further replace $\psi_2$ by $\fgt_{x_1}^\st \psi_2$. Then the left-hand side of \eqref{step 4 recursion} has all its insertions pulled back along $\fgt_{x_1}$ and so we may apply the projection formula to identify this with a (recursively-known) absolute invariant of $Y$. Now examine the right-hand side. There is a locus where the curve breaks as follows
\begin{center}
\begin{tikzpicture}[scale=1]
%edge
\draw (0,0) to (2,0);
\draw [color=blue] (1,0) node[below]{\tiny$\alpha_1$};

%C_1
\draw [fill=black] (0,0) circle[radius=3pt];
\draw (0,-0.1) node[below]{\small$0$};

%x_0
\draw [->] (0,0) -- (0,1);
\draw (0,0.9) node[left]{$x_0$};
\draw [color=blue] (0,0.5) node[right]{\tiny$0$};

%x_1
\draw [->] (0,0) -- (-1.5,0);
\draw (-1.5,0) node[above]{\small$x_1$};
\draw [color=blue](-0.75,0) node[below]{\tiny$\alpha_1$};

%y
\draw [->] (2,0) -- (2,1);
\draw (2,0.9) node[left]{$y$};
\draw [color=blue] (2,0.5) node[right]{\tiny$0$};

%C_0
\draw [fill=white] (2,0) circle[radius=3pt];
\draw (2,-0.1) node[below]{\small$\alpha_1$};

%target
\draw [color=blue] (0,-1) to (2,-1);
\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
\draw [fill=blue,color=blue] (2,-1) circle[radius=3pt];
\draw [color=blue,->] (2,-1) -- (3,-1);
\draw [color=blue,->] (0,-1) -- (-1,-1);
\end{tikzpicture}
\end{center}
with all other markings concentrated on the genus one piece. The contribution of this locus is given by
\begin{equation*} \alpha_1 \cdot \psi_y \cdot \gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty)]_{\Gm} \end{equation*}
and by the dilaton equation for reduced rubber invariants (see \S \ref{}) we may identify this with a (nonzero) multiple of the invariant $I$ we are trying to compute (note that $\psi_y = \hat\psi_y$ because $y$ is a non-relative marking).

Now consider the other loci which contribute to the right-hand side of \eqref{step 4 recursion}. Their contributions are recursively known except for when one of the curve pieces $C^\prime$ has degree $d$ and $n$ relative points. If $C^\prime$ is mapped to the bottom level of the expanded target, then we may apply the projection formula with $\fgt_{x_1}$ to identify the contribution with an absolute invariant of $Y$. If $C^\prime$ is mapped to the top level, then we must have $x_1$ contained in a collapsed rational bubble on the left-hand side. This bubble has at most three special points; any more and the projection formula with $\fgt_{x_1}$ will cause the contribution to vanish. Thus the bubble contains at most one non-relative marking.

[DOESN'T SEEM LIKE WE CAN CONTROL THIS?]

>>>>

[TO BE FINISHED]
